### 2018-05-17 manuscript.rmd
adjusted wording

Ancestral character state reconstructions favor the hypothesis that monoecy arose twice (Fig. \@ref(reconstruct)A, \@ref(fig:BI-mono)), once in Calycophorae and once in Clade A. This is consistent with differences in the arrangements of male and female gonophores in the two clades. In Clade A, male and female zooids are found within the same cormidium (a single reiterated sequence of zooids along the stem, see Fig. \@ref(colony)). In these species, the male and female zooids are placed at different but well defined locations within the cormidium. Meanwhile in calycophorans, each cormidium bears either male or female gonophores. In this form of monoecy, the male and female cormidia can either occur in an alternating pattern, or there can be several male or female cormidia in a row. In either case, male and female zooids are found at the same corresponding locations within the cormidia. One exception to this is Abylids, where both male or female gonophores may be found within the same eudoxid [@carre1967]. In sum, homoplasy in sexual-system evolution along with variation in the spatial arrangement of gonophores within a colony suggest that siphonophores have evolved different ways to be monoecious. The sexual system and cormidial arrangement of *Rudjakovia* is undescribed, although preliminary observations suggest that this species may be monoecious and that monoecy arose a third time in the Pyrostephidae. A detailed redescription of *Rudjakovia* would help clarify this.

@@

Bracts are greatly reduced zooids unique to siphonophores, where they are only present in Codonophora (Fig. \@ref(traitdist)). Bracts are functional for protection of the delicate zooids and to help maintain neutral buoyancy [@jacobs1937beobachtungen]. Some calycophorans are able to actively exclude sulphate ions in their bracts to adjust their buoyancy along the colony [@bidigare1980role]. Bracts were lost in Hippopodiidae, some clausophyids, *Physophora hydrostatica* (Fig. \@ref(siphonophores)K), and in *Gymnopraia lapislazula*. These patterns of loss are not captured in this study, as most of these species are not included in the present phylogeny. In species without bracts, other zooids appear to fulfill the roles of neutral buoyancy and protection. In *P. hydrostatica*, enlarged palpons surround all other siphosomal zooids and move in a coordinated manner to inflict a powerful sting [@totton1965synopsis]. While in *Hippopodius hippopus* the nectophores play a role in maintaining neutral buoyancy and possibly also in defense, by bioluminescing and blanching in response to stimuli (Fig. \@ref(siphonophores)C shows the blanching of nectophores)[@bassot1978bioluminescence].

>>>>

Ancestral character state reconstructions favor the hypothesis that monoecy arose twice (Fig. \@ref(reconstruct)A, \@ref(fig:BI-mono)), once in Calycophorae and once in Clade A. This is consistent with differences in the arrangements of male and female gonophores in the two clades. In Clade A, male and female zooids are found within the same cormidium (a single reiterated sequence of zooids along the stem, see Fig. \@ref(colony)). In these species, the male and female zooids are placed at different but well defined locations within the cormidium. Meanwhile in calycophorans, each cormidium bears either male or female gonophores. In this form of monoecy, the male and female cormidia can either occur in an alternating pattern, or there can be several male or female cormidia in a row. In either case, male and female zooids are found at the same corresponding locations within the cormidia. One known exception to this can be found in abylid calycophorans, where both male or female gonophores may be found within the same eudoxid [@carre1967]. In sum, homoplasy in sexual-system evolution along with variation in the spatial arrangement of gonophores within a colony suggest that siphonophores have evolved different ways to be monoecious. The sexual system and cormidial arrangement of *Rudjakovia* is undescribed, although preliminary observations suggest that this species may be monoecious and that monoecy arose a third time in the Pyrostephidae. A detailed redescription of *Rudjakovia* would help clarify this.

@@

Bracts are greatly reduced zooids unique to siphonophores, where they are only present in Codonophora (Fig. \@ref(traitdist)). Bracts are functional for protection of the delicate zooids and to help maintain neutral buoyancy [@jacobs1937beobachtungen]. Some calycophorans are able to actively exclude sulphate ions in their bracts to adjust their buoyancy along the colony [@bidigare1980role]. Bracts were lost in Hippopodiidae, some clausophyids, *Physophora hydrostatica* (Fig. \@ref(siphonophores)K), and in *Gymnopraia lapislazula*. These patterns of loss are not captured in this study, as most of these species are not included in the present phylogeny. In species without bracts, other zooids appear to fulfill the roles of buoyancy control and protection. In *P. hydrostatica*, enlarged palpons surround all other siphosomal zooids and move in a coordinated manner to inflict a powerful sting [@totton1965synopsis]. While in *Hippopodius hippopus* the nectophores play a role in maintaining neutral buoyancy and possibly also in defense, by bioluminescing and blanching in response to stimuli (Fig. \@ref(siphonophores)C shows the blanching of nectophores)[@bassot1978bioluminescence].
